---
title: "Data Analysis Hexad-12 Spanish"
output: html_document
date: "2025-11-28"
---

```{r setup, echo = FALSE}
knitr::opts_chunk$set(echo = FALSE,warning = FALSE, message = FALSE)

#---
#title: "README"
#output: 
#  github_document:
#    pandoc_args: ["--wrap=none"]
#always_allow_html: true
#---

#---
#title: "Data Analysis Hexad-12 Spanish"
#output: html_document
#date: "2025-11-28"
#---


```

```{r,warning = FALSE, message = FALSE, echo=FALSE, include=FALSE}
# Load required libraries
# List of libraries to check, install (if missing), and load
libraries <- c(
  "knitr", "dplyr", "ggplot2", "tidyr", "multcomp", 
  "kableExtra", "FSA", "MVN", "lavaan", "semPlot", 
  "psych", "boot", "markdown","moments","tidyverse","gghalves", "multimode"
)


# Function to check, install, and load libraries
check_and_load <- function(lib) {
  if (!require(lib, character.only = TRUE)) {
    install.packages(lib, dependencies = TRUE)
    library(lib, character.only = TRUE)
  }
}

# Apply the function to all libraries
lapply(libraries, check_and_load)
set.seed(123)  # For reproducibility
num_bootstrap <- 10000 # Number of bootstrap samples

```


```{r}
# Define the GitHub raw CSV URL
#github_url <- "https://raw.githubusercontent.com//Hexad-/refs/heads/main/Hexad_12_Spanish_data.csv"

# Define a local file path to save the downloaded file
#local_file <- tempfile(fileext = ".csv")

# Download the file
#download.file(github_url, local_file)

# Load the CSV into a data frame
#data <- read.csv(local_file,row.names = 1)
data<-read.csv("Hexad_12_Spanish_data.csv")

# Display the first few rows of the data frame
head(data)
```

# 4. Results

## Sample descriptives

### Number of Participants

Each row represents a data point from a single participant. Total number of participants

```{r}
print(nrow(data))
```

### Completion Time Summary statistics

```{r}
# Ensure Completion.Time is numeric
data$Completion.Time <- as.numeric(data$Completion.Time)

# Compute and create summary table
summary_table <- data.frame(
  Statistic = c("Average", "Median", "Min", "Max", "Standard Deviation", "Non-Empty Rows"),
  Value = c(
   round(mean(data$Completion.Time, na.rm = TRUE),2),
    round(median(data$Completion.Time, na.rm = TRUE),2),
    round(min(data$Completion.Time, na.rm = TRUE),2),
    round(max(data$Completion.Time, na.rm = TRUE),2),
    round(sd(data$Completion.Time, na.rm = TRUE),2),
    round(sum(!is.na(data$Completion.Time)),0)
  )
)

# Display the table
kable(summary_table, caption = "Summary Statistics for Completion Time")
```

### Age Summary statistics

```{r}
data$Age <- as.numeric(data$Age)

# Compute and create summary table
summary_table <- data.frame(
  Statistic = c("Average", "Median", "Min", "Max", "Standard Deviation", "Non-Empty Rows"),
  Value = c(
   round(mean(data$Age, na.rm = TRUE),2),
    round(median(data$Age, na.rm = TRUE),2),
    round(min(data$Age, na.rm = TRUE),2),
    round(max(data$Age, na.rm = TRUE),2),
    round(sd(data$Age, na.rm = TRUE),2),
    round(sum(!is.na(data$Age)),0)
  )
)

# Display the table
kable(summary_table, caption = "Summary Statistics for Age")
```

### Gender Summary statistics

```{r}
# Encode Gender as a factor with specific levels
gender_labels <- c("female", "male", "other")
data$Gender <- factor(data$Gender, levels = gender_labels)

# Compute summary statistics for Gender
gender_counts <- table(data$Gender)
total_count <- sum(gender_counts)
gender_percentages <- round((gender_counts / total_count) * 100, 2)

# Create a summary table
gender_summary_table <- data.frame(
  Gender = c(names(gender_counts), "Total"),
  Count = c(as.numeric(gender_counts), total_count),
  Percentage = c(paste0(gender_percentages, "%"), "100%")
)

# Display the table
kable(gender_summary_table, caption = "Summary of Gender Distribution with Totals")

```

### Education Level Summary statistics

```{r}
# Encode Education Level as a factor with specific levels
educationlevel_labels <- c(
  "High School diploma",
  "Technical or vocational training",
  "Associate's degree",
  "Bachelor's degree",
  "Master's degree",
  "Professional degree",
  "Doctorate"
)

data$Education <- factor(data$Education, levels = educationlevel_labels)

# Compute counts and percentages
education_counts <- table(data$Education)
total_count <- sum(education_counts)
education_percentages <- round((education_counts / total_count) * 100, 2)

# Create a summary table
education_summary_table <- data.frame(
  EducationLevel = c(names(education_counts), "Total"),
  Count = c(as.numeric(education_counts), total_count),
  Percentage = c(paste0(education_percentages, "%"), "100%")
)

# Display the summary table
kable(education_summary_table, caption = "Summary of Education Level Distribution with Totals")
```

### Game frequency Summary statistics

```{r}
data$Freq.Games <- as.numeric(data$Freq.Games)

# Compute and create summary table
summary_table <- data.frame(
  Statistic = c("Average", "Median", "Min", "Max", "Standard Deviation", "Non-Empty Rows"),
  Value = c(
   round(mean(data$Freq.Games, na.rm = TRUE),2),
    round(median(data$Freq.Games, na.rm = TRUE),2),
    round(min(data$Freq.Games, na.rm = TRUE),2),
    round(max(data$Freq.Games, na.rm = TRUE),2),
    round(sd(data$Freq.Games, na.rm = TRUE),2),
    round(sum(!is.na(data$Freq.Games)),0)
  )
)

# Display the table
kable(summary_table, caption = "Summary Statistics for Frequency of Play")
```

### Country of Origin Summary statistics

```{r}
# Filter the data to exclude empty Country values
filtered_data <- data$Country[data$Country != ""]

# Compute counts and percentages
country_counts <- sort(table(filtered_data), decreasing = TRUE)
total_count <- sum(country_counts)
country_percentages <- round((country_counts / total_count) * 100, 2)

# Create a summary table with "Total" as the first row
summary_table <- data.frame(
  Country = c("Total", names(country_counts)),
  Count = c(total_count, as.numeric(country_counts)),
  Percentage = c("100%", paste0(country_percentages, "%"))
)

# Display the summary table
kable(head(summary_table,11), caption = "Summary of Country Distribution with Totals at the Top")

```

### Hexad determinants Summary statistics

#### Table 4. Summary Statistics of Hexad-12 determinants (N = 866)

```{r}


# Subset data to include the first six columns
subdata <- data[, c(2:7)]

# Specify the columns of interest
columns_of_interest <- c("Philanthropist", "Socializer", "Free Spirit", "Achiever", "Player", "Disruptor")

# Rename columns
colnames(subdata) <- columns_of_interest

# Calculate summary statistics and round to 2 decimal places
summary_stats <- data.frame(
  Column   = columns_of_interest,
  Mean     = round(sapply(subdata[columns_of_interest], mean,      na.rm = TRUE), 2),
  Median   = round(sapply(subdata[columns_of_interest], median,    na.rm = TRUE), 2),
  Min      = round(sapply(subdata[columns_of_interest], min,       na.rm = TRUE), 2),
  Max      = round(sapply(subdata[columns_of_interest], max,       na.rm = TRUE), 2),
  SD       = round(sapply(subdata[columns_of_interest], sd,        na.rm = TRUE), 2),
  Skewness = round(sapply(subdata[columns_of_interest], skewness,  na.rm = TRUE), 2),
  Kurtosis = round(sapply(subdata[columns_of_interest], moments::kurtosis,  na.rm = TRUE), 2)
)

# Sort by descending Mean
summary_stats <- summary_stats[order(-summary_stats$Mean), ]

# Print the table nicely with knitr::kable
kable(summary_stats, 
      caption = "Summary Statistics of Hexad-12 determinants", 
      digits  = 2)


```

#### Figure 1: Violin plot of Hexad determinant distributions

```{r}

library(tidyverse)
library(gghalves)
library(dplyr)
# ---- reshape to long form ---------------------------------------------------
hexad_long <- data %>% 
  dplyr::select(
    Philanthropist = 'philanthropist',
    Socializer     = 'socializer',
    `Free Spirit`  = 'freeSpirit',
    Achiever       = 'achiever',
    Player         = 'player',
    Disruptor      = 'disruptor'
  ) %>% 
  pivot_longer(
    cols      = everything(),
    names_to  = "Determinant",
    values_to = "Score"
  ) %>% 
  mutate(
    Determinant = fct_reorder(Determinant, Score, .fun = mean, .desc = TRUE)
  )

```
```{r}
library(tidyverse)
library(gghalves)
library(dplyr)
library(forcats)

# ---- Reshape to long form ---------------------------------------------------
hexad_long <- data %>%
  dplyr::select(
    Philanthropist = philanthropist,
    Socializer     = socializer,
    `Free Spirit`  = freeSpirit,
    Achiever       = achiever,
    Player         = player,
    Disruptor      = disruptor
  ) %>%
  pivot_longer(
    cols      = everything(),
    names_to  = "Determinant",
    values_to = "Score"
  ) %>%
  mutate(
    Determinant = fct_reorder(
      Determinant,
      Score,
      .fun = mean,
      .desc = TRUE,
      na.rm = TRUE
    )
  )

# ---- Violin plot, boxplot, and jittered observations ------------------------
g <- ggplot(
  hexad_long,
  aes(x = Determinant, y = Score, fill = Determinant)
) +
  geom_violin(
    trim = FALSE,
    width = 0.95,
    alpha = 0.60,
    linewidth = 0.5
  ) +
  geom_boxplot(
    width = 0.10,
    fill = "white",
    linewidth = 0.7,
    outlier.shape = NA
  ) +
  geom_jitter(
    aes(color = Determinant),
    width = 0.10,
    height = 0.08,
    size = 1.2,
    alpha = 0.18,
    show.legend = FALSE
  ) +
  scale_y_continuous(
    limits = c(2, 14),
    breaks = seq(2, 14, by = 2),
    minor_breaks = NULL,
    expand = expansion(mult = c(0.01, 0.03))
  ) +
  guides(fill = "none") +
  labs(
    title = "Distribution of Hexad Motivational Determinants",
    x = NULL,
    y = "Summed determinant score (2–14)"
  ) +
  theme_classic(base_size = 16) +
  theme(
    # Figure title
    plot.title = element_text(
      size = 18,
      face = "bold",
      hjust = 0.5,
      margin = margin(b = 14)
    ),

    # Axis title
    axis.title.y = element_text(
      size = 16,
      face = "bold",
      margin = margin(r = 12)
    ),

    # Axis tick labels
    axis.text.x = element_text(
      size = 14,
      face = "bold",
      angle = 0,
      hjust = 0.5,
      margin = margin(t = 8)
    ),
    axis.text.y = element_text(
      size = 14,
      face = "bold"
    ),

    # Axis ticks and lines
    axis.ticks = element_line(linewidth = 0.7),
    axis.ticks.length = unit(0.18, "cm"),
    axis.line = element_line(linewidth = 0.8),

    # Add horizontal guides while keeping the figure uncluttered
    panel.grid.major.y = element_line(
      linewidth = 0.35,
      linetype = "dashed"
    ),
    panel.grid.major.x = element_blank(),

    # Margins around the complete figure
    plot.margin = margin(
      t = 12,
      r = 14,
      b = 12,
      l = 14
    )
  )

print(g)

# ---- Export at publication quality -----------------------------------------
ggsave(
  filename = "Figure2_Hexad_distributions.png",
  plot = g,
  width = 9,
  height = 6,
  units = "in",
  dpi = 600,
  bg = "white"
)

# Optional vector version, useful if accepted by the journal
ggsave(
  filename = "Figure2_Hexad_distributions.pdf",
  plot = g,
  width = 9,
  height = 6,
  units = "in",
  device = cairo_pdf
)
```

### Summary statistics for all Hexad-12 determinants across key subgroups


#### Appendix A1. Distribution of Hexad determinants by Age Group

```{r}
library(dplyr)
library(tidyr)

# Hexad determinants
hexad_vars <- c("philanthropist", "socializer", "freeSpirit",
                "achiever", "player", "disruptor")

# Create age groups
data_age <- data %>%
  filter(!is.na(Age)) %>%                 
  mutate(
    AgeGroup = case_when(
      Age >= 18 & Age <= 24 ~ "18–24",
      Age >= 25 & Age <= 34 ~ "25–34",
      Age >= 35 & Age <= 49 ~ "35–49",
      Age >= 50             ~ "50+"
    )
  ) %>%
  filter(!is.na(AgeGroup))

# Summaries per age group
hexad_by_age <- data_age %>%
  group_by(AgeGroup) %>%
  summarise(
    N = n(),
    across(
      all_of(hexad_vars),
      list(
        Mean   = ~mean(., na.rm = TRUE),
        Median = ~median(., na.rm = TRUE),
        Min    = ~min(., na.rm = TRUE),
        Max    = ~max(., na.rm = TRUE),
        SD     = ~sd(., na.rm = TRUE)
      ),
      .names = "{.col}_{.fn}"
    ),
    .groups = "drop"
  ) %>%
  # Round all numeric columns except N
  mutate(across(where(is.numeric) & !matches("^N$"), ~round(.x, 2)))

# Flip table so rows = stats, columns = age groups
hexad_by_age_flipped <- hexad_by_age %>%
  pivot_longer(
    cols = -AgeGroup,
    names_to = "Measure",
    values_to = "Value"
  ) %>%
  pivot_wider(
    names_from = AgeGroup,
    values_from = Value
  )




kable(hexad_by_age_flipped, 
      caption = " Distribution of Hexad determinants by Age Group", 
      digits  = 2)
```

#### Appendix A2. Distribution of Hexad determinants by Gender

```{r}
library(dplyr)
library(tidyr)

# Hexad determinants
hexad_vars <- c("philanthropist", "socializer", "freeSpirit",
                "achiever", "player", "disruptor")

# Summaries by Gender (exclude missing Gender)
hexad_by_gender <- data %>%
  filter(!is.na(Gender)) %>%      # drop NA genders
  group_by(Gender) %>%
  summarise(
    N = n(),                      # sample size per gender
    across(
      all_of(hexad_vars),
      list(
        Mean   = ~mean(., na.rm = TRUE),
        Median = ~median(., na.rm = TRUE),
        Min    = ~min(., na.rm = TRUE),
        Max    = ~max(., na.rm = TRUE),
        SD     = ~sd(., na.rm = TRUE)
      ),
      .names = "{.col}_{.fn}"
    ),
    .groups = "drop"
  ) %>%
  # Round all numeric columns except N
  mutate(across(where(is.numeric) & !matches("^N$"), ~round(.x, 2)))

# Flip table so:
#    - Rows = N, philanthropist_Mean, ..., disruptor_SD
#    - Columns = Gender values
hexad_by_gender_flipped <- hexad_by_gender %>%
  pivot_longer(
    cols = -Gender,
    names_to = "Measure",
    values_to = "Value"
  ) %>%
  pivot_wider(
    names_from = Gender,
    values_from = Value
  )



kable(hexad_by_gender_flipped, 
      caption = "Distribution of Hexad determinants by Gender", 
      digits  = 2)

```


#### Appendix A3. Distribution of Hexad determinants by Education

```{r}
library(dplyr)
library(tidyr)

# Hexad determinants
hexad_vars <- c("philanthropist", "socializer", "freeSpirit",
                "achiever", "player", "disruptor")

# 1) Summaries by Education (with N)
hexad_by_edu <- data %>%
  filter(!is.na(Education)) %>%        
  group_by(Education) %>%
  summarise(
    N = n(),
    across(
      all_of(hexad_vars),
      list(
        Mean   = ~mean(., na.rm = TRUE),
        Median = ~median(., na.rm = TRUE),
        Min    = ~min(., na.rm = TRUE),
        Max    = ~max(., na.rm = TRUE),
        SD     = ~sd(., na.rm = TRUE)
      ),
      .names = "{.col}_{.fn}"
    ),
    .groups = "drop"
  ) %>%
  # Round all numeric columns except N
  mutate(across(where(is.numeric) & !matches("^N$"), ~round(.x, 2)))

# 2) Flip the table
hexad_by_edu_flipped <- hexad_by_edu %>%
  pivot_longer(
    cols = -Education,
    names_to = "Measure",
    values_to = "Value"
  ) %>%
  pivot_wider(
    names_from = Education,
    values_from = Value
  )

# Print the table nicely with knitr::kable
kable(hexad_by_edu_flipped, 
      caption = "Distribution of Hexad determinants by Education", 
      digits  = 2)

```

#### Apendix A4. Distribution of Hexad determinants by Weekly Gaming Frequency

```{r}
library(dplyr)
library(tidyr)

# Hexad determinants
hexad_vars <- c("philanthropist", "socializer", "freeSpirit",
                "achiever", "player", "disruptor")

# Create game-frequency groups
data_freq <- data %>%
  filter(!is.na(Freq.Games)) %>%  
  mutate(
    FreqGroup = case_when(
      Freq.Games >= 1 & Freq.Games <= 2 ~ "1–2 days",
      Freq.Games >= 3 & Freq.Games <= 4 ~ "3–4 days",
      Freq.Games >= 5 & Freq.Games <= 7 ~ "5–7 days"
    )
  ) %>%
  filter(!is.na(FreqGroup))

# Summaries per frequency group
hexad_by_freq <- data_freq %>%
  group_by(FreqGroup) %>%
  summarise(
    N = n(),
    across(
      all_of(hexad_vars),
      list(
        Mean   = ~mean(., na.rm = TRUE),
        Median = ~median(., na.rm = TRUE),
        Min    = ~min(., na.rm = TRUE),
        Max    = ~max(., na.rm = TRUE),
        SD     = ~sd(., na.rm = TRUE)
      ),
      .names = "{.col}_{.fn}"
    ),
    .groups = "drop"
  ) %>%
  mutate(across(where(is.numeric) & !all_of("N"), ~round(.x, 2)))

# Flip table: rows = stats, columns = freq groups
hexad_by_freq_flipped <- hexad_by_freq %>%
  pivot_longer(
    cols = -FreqGroup,
    names_to  = "Measure",
    values_to = "Value"
  ) %>%
  pivot_wider(
    names_from  = FreqGroup,
    values_from = Value
  )




kable(hexad_by_freq_flipped, 
      caption = " Distribution of Hexad determinants by Weekly Gaming Frequency", 
      digits  = 2)

```


#### Appendix A5. Distribution of Hexad items by Country

```{r}
#Shorten Countries Name for easy of tables
data[data$Country=="Bolivia (Estado Plurinacional de)", 'Country' ]<-"Bolivia"
data[data$Country=="Venezuela (República Bolivariana de)", 'Country' ]<-"Venezuela"
data[data$Country==" Estados Unidos de América", 'Country' ]<-"USA"
data$Country<-as.factor(data$Country)

# Filter out rows where 'Country' is missing
hexad_data_clean <- data %>% filter(Country != "")

# Identify the top 5, top 10, and top 20 most common countries
top_countries <- hexad_data_clean %>%
  count(Country, sort = TRUE)

top_10_countries <- top_countries %>% slice(1:10) %>% pull(Country)

# Filter data for these top countries
hexad_top10 <- hexad_data_clean %>% filter(Country %in% top_10_countries)






# Calculate and round summary statistics by Country for each player type
hexad_summary <- hexad_top10 %>%
  group_by(Country) %>%
  summarise(
    sample_size = n(),
    philanthropist_mean = round(mean(philanthropist, na.rm = TRUE), 2),
    philanthropist_median = round(median(philanthropist, na.rm = TRUE), 2),
    philanthropist_min = round(min(philanthropist, na.rm = TRUE), 2),
    philanthropist_max = round(max(philanthropist, na.rm = TRUE), 2),
    philanthropist_sd = round(sd(philanthropist, na.rm = TRUE), 2),
    
    socializer_mean = round(mean(socializer, na.rm = TRUE), 2),
    socializer_median = round(median(socializer, na.rm = TRUE), 2),
    socializer_min = round(min(socializer, na.rm = TRUE), 2),
    socializer_max = round(max(socializer, na.rm = TRUE), 2),
    socializer_sd = round(sd(socializer, na.rm = TRUE), 2),
    
    freeSpirit_mean = round(mean(freeSpirit, na.rm = TRUE), 2),
    freeSpirit_median = round(median(freeSpirit, na.rm = TRUE), 2),
    freeSpirit_min = round(min(freeSpirit, na.rm = TRUE), 2),
    freeSpirit_max = round(max(freeSpirit, na.rm = TRUE), 2),
    freeSpirit_sd = round(sd(freeSpirit, na.rm = TRUE), 2),
    
    achiever_mean = round(mean(achiever, na.rm = TRUE), 2),
    achiever_median = round(median(achiever, na.rm = TRUE), 2),
    achiever_min = round(min(achiever, na.rm = TRUE), 2),
    achiever_max = round(max(achiever, na.rm = TRUE), 2),
    achiever_sd = round(sd(achiever, na.rm = TRUE), 2),
    
    player_mean = round(mean(player, na.rm = TRUE), 2),
    player_median = round(median(player, na.rm = TRUE), 2),
    player_min = round(min(player, na.rm = TRUE), 2),
    player_max = round(max(player, na.rm = TRUE), 2),
    player_sd = round(sd(player, na.rm = TRUE), 2),
    
    disruptor_mean = round(mean(disruptor, na.rm = TRUE), 2),
    disruptor_median = round(median(disruptor, na.rm = TRUE), 2),
    disruptor_min = round(min(disruptor, na.rm = TRUE), 2),
    disruptor_max = round(max(disruptor, na.rm = TRUE), 2),
    disruptor_sd = round(sd(disruptor, na.rm = TRUE), 2)
  ) %>%
  arrange(desc(sample_size)) # Sort by sample size

# Transpose the table
hexad_summary_t <- hexad_summary %>%
  pivot_longer(cols = -Country, names_to = "Statistic", values_to = "Value") %>%
  pivot_wider(names_from = Country, values_from = Value)

# Generate an RMarkdown table
hexad_summary_t %>%
  kbl(caption = "Transposed Summary Statistics for Hexad Player Types by Country") %>%
  kable_styling(full_width = TRUE, bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```


## 4.1 Item-level diagnostics

#### Appendix A8. Summary Statistics per item

```{r}

merged_hexad<-data
item_cols <- c("A2","A4","D3","D4","F1","F3","P1","P4","R2","R4","S2","S4")
df_items  <- merged_hexad[ , item_cols ]

# Descriptive statistics
desc_stats <- describe(df_items)

kable(desc_stats, caption = "Summary Statistics per item",digits  = 2)





```



#### Appendix A9. Mardia’s multivariate normality test for Hexad-12 items

```{r}

# Perform Mardia's test for multivariate normality
mardia_test <- mvn(data = data[, 7:18], mvnTest = "mardia")
mardia_test_N<-mardia_test$multivariateNormality
# Extract and prepare the results for the table
mardia_results <- data.frame(
  Test = c("Skewness", "Kurtosis"),
  Statistic = c(
    (mardia_test_N[1,2]),
    (mardia_test_N[2,2])
    
  ),
  P_Value = c(
  (mardia_test_N[1,3]),
    (mardia_test_N[2,3])
    
  )
)

# Create and display the RMarkdown table
mardia_results %>%
  kbl(caption = "Mardia's Test for Multivariate Normality") %>%
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```

#### Appendix A10. Response distributions for each Hexad-12 item

```{r}

item_cols <- c("A2","A4","D3","D4","F1","F3","P1","P4","R2","R4","S2","S4")
df_items <- merged_hexad[, item_cols]

# Reshape to long format for plotting
df_long <- df_items %>%
  pivot_longer(cols      = everything(),
               names_to  = "item",
               values_to = "score")

# Faceted histograms
ggplot(df_long, aes(x = score)) +
  geom_histogram(bins = 30, color = "black", fill = "lightblue") +
  facet_wrap(~ item, scales = "free") +
  labs(title = "Hexad-12 Item Distributions",
       x     = "Response",
       y     = "Count") +
  theme_minimal()


```

#### Appendix A11. Multimodality Silverman tests results

```{r, cache=TRUE}


set.seed(123)  # For reproducibility

for(it in item_cols) {
  x <- na.omit(merged_hexad[[it]])
  # Silverman’s test (mod0=1 ⇒ test unimodality vs. multimodality)
  si <- modetest(x, mod0 = 1, method = "SI", B = num_bootstrap)
  
  cat(sprintf(
    "%-3s  bw = %.3f  p = %.3f\n",
    it,
    si$statistic,   # critical bandwidth
    si$p.value      # p-value
  ))
}
```

#### Appendix A12. Item–total correlation for each subscale

```{r}

# Item–total correlations
merged_hexad$total_score <- rowSums(df_items, na.rm=TRUE)
item_total_corrs <- map_dbl(item_cols, ~ cor(
  merged_hexad[[.x]],
  merged_hexad$total_score - merged_hexad[[.x]],
  use = "pairwise.complete.obs"
))
names(item_total_corrs) <- item_cols



kable(item_total_corrs, caption = "Item–total correlation for each subscale",digits  = 2)
```

## 4.2. Confirmatory Factor Analysis

#### Table 5: Estimated factor loadings for Hexad-12 items

```{r}
# Specify the CFA model
cfa_model <- '
  Achiever =~ A2 + A4
  Disruptor =~ D3 + D4
  FreeSpirit =~ F1 + F3
  Philanthropist =~ P1 + P4
  Player =~ R2 + R4
  Socializer =~ S2 + S4
'

# Fit the CFA model
fit <- cfa(cfa_model, data = data,std.lv=TRUE, estimator = "WLSMV")  #auto.efa = TRUE
 #
# Global Fit Metrics
results<-summary(fit, fit.measures = TRUE, standardized = TRUE, rsquare = TRUE)

kable(
  results$pe[1:12, c(2:8, 10)],
  caption = "Estimated factor loading for Hexad-12 items",
  digits  = 3,
  format = "html"
) %>%
  kable_styling(full_width = TRUE) %>%
  column_spec(1:ncol(results$pe[1:12, c(2:8, 10)]), width = "2cm")



```

#### CFA

```{r}
# Confirmatory Factor Analysis
model <- '
  Achiever       =~ A2 + A4
  Disruptor      =~ D3 + D4
  FreeSpirit     =~ F1 + F3
  Philanthropist =~ P1 + P4
  Player         =~ R2 + R4
  Socializer     =~ S2 + S4
'
fit <- cfa(model, data = merged_hexad, estimator = "WLSMV")
#summary(fit, fit.measures = TRUE, standardized = TRUE)
```

#### Figure 2. Standardized CFA model

```{r}
pdf(
  "Hexad12_CFA_plot.pdf",
  width = 14,
  height = 14,
  family = "sans"
)

semPlot::semPaths(
  fit,

  # Uniform paths with standardized coefficient labels
  what = "paths",
  whatLabels = "std",
  nDigits = 2,

  # Layout
  layout = "tree2",
  rotation = 2,
  centerLevels = TRUE,
  cardinal = "all",

  # More vertical space between levels/rows
  layoutScale = c(1.20, 1.70),

  # Remove unnecessary model elements
  residuals = FALSE,
  intercepts = FALSE,
  thresholds = FALSE,
  exoVar = FALSE,
  exoCov = FALSE,

  # Nodes and text
  nCharNodes = 0,
  sizeMan = 9,
  sizeLat = 13,
  label.cex = 1.25,
  label.scale.equal = TRUE,

  # Node appearance
  color = list(lat = "white", man = "white"),
  borders = TRUE,
  border.width = 1.5,

  # Force all paths to be solid black
  edge.color = "black",
  edge.width = 1.3,
  fixedStyle = c("black", 1),
  freeStyle = c("black", 1),
  negDashed = FALSE,
  fade = FALSE,
  curve = 0,

  # Arrows
  asize = 2,
  arrowAngle = pi / 8,

  # Coefficient labels
  edge.label.cex = 1.10,
  edge.label.position = 0.58,
  edge.label.color = "black",

  title = FALSE,
  mar = c(10, 8, 10, 8)
)

dev.off()
```

#### Table 6: CFA fit indices with 95% CI using bootstrapping with 10,000 samples

```{r, cache=TRUE}


reliability_metrics <- semTools::reliability(fit)
CR<-reliability_metrics[2,]
AVE<-reliability_metrics[5,]
  

  # Extract relevant fit measures
  fit_measures_final <- fitMeasures(fit,standardized = TRUE, rsquare = TRUE, c("chisq.scaled", "srmr", "tli.scaled", "cfi.scaled", "rmsea.scaled"))

  fit_measures_final<-c(fit_measures_final, CR, AVE)
  

# Function to take a bootstrap sample and perform CFA, returning CR, Omega, and AVE
bootstrap_cfa_cr_omega_ave <- function(data, cfa_model) {
  # Generate a bootstrap sample (with replacement)
  bootstrap_sample <- data[sample(1:nrow(data), replace = TRUE), ]
  

# Fit the CFA model
fit <- cfa(cfa_model, data = bootstrap_sample,std.lv=TRUE, auto.efa = TRUE, estimator = "WLSMV")

 # Calculate reliability metrics (including Composite Reliability)
reliability_metrics <- semTools::reliability(fit)
  CR<-reliability_metrics[2,]
 AVE<-reliability_metrics[5,]
  

  # Extract relevant fit measures
  fit_measures <- fitMeasures(fit, c("chisq.scaled", "srmr", "tli.scaled", "cfi.scaled", "rmsea.scaled"))

  fit_measures<-c(fit_measures, CR, AVE)
 
  return(fit_measures)
}

# Perform bootstrap sampling
set.seed(123)  # For reproducibility


# Initialize matrix to store CR, Omega, and AVE
fit_metrics <- matrix(NA, nrow = num_bootstrap, ncol = 17)
# List of columns to calculate confidence intervals for
columns_to_ci <- c("chisq.scaled", "srmr", "tli.scaled", "cfi.scaled", "rmsea.scaled", 
                   "CR.Achiever", "CR.Disruptor", "CR.FreeSpirit", "CR.Philanthropist", 
                   "CR.Player", "CR.Socializer", 
                   "AVE.Achiever", "AVE.Disruptor", "AVE.FreeSpirit", 
                   "AVE.Philanthropist", "AVE.Player", "AVE.Socializer")
colnames(fit_metrics) <- columns_to_ci

# Bootstrap loop
for (i in 1:num_bootstrap) {
  fit_metrics[i, ] <- bootstrap_cfa_cr_omega_ave(data, cfa_model)
}


  names(fit_measures_final) <- columns_to_ci


# Initialize an empty data frame to store the results
results_table <- data.frame(
  Metric = columns_to_ci,
  Estimate = numeric(length(columns_to_ci)),
  CI_Lower = numeric(length(columns_to_ci)),
  CI_Upper = numeric(length(columns_to_ci)),
  stringsAsFactors = FALSE
)

# Populate the results table with confidence intervals and estimates
for (i in seq_along(columns_to_ci)) {
  col <- columns_to_ci[i]
  ci <- quantile(fit_metrics[, col], probs = c(0.025, 0.975))
  results_table$Estimate[i] <- round(fit_measures_final[col], 3)  # Add the estimate and round
  results_table$CI_Lower[i] <- round(ci[1], 3)  # Round lower CI
  results_table$CI_Upper[i] <- round(ci[2], 3)  # Round upper CI
}

# Correctly print the table in a nicely formatted way
results_table %>%
  kbl(caption = "CFA  metrics with confident interval", format = "markdown",digits  = 3) %>%
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```

######## Table 6: CFA fit indices with 95% CI using bootstrapping with 10,000 samples (Sensitivy analysis:without "fast_responders" \< 52.28sec )

```{r, cache=TRUE}

hexad_data_52<-data[data$Completion.Time>52.28, ]
dim(hexad_data_52)
# Function to take a bootstrap sample and perform CFA, returning CR, Omega, and AVE
bootstrap_cfa_cr_omega_ave <- function(data, cfa_model) {
  # Generate a bootstrap sample (with replacement)
  bootstrap_sample <- data[sample(1:nrow(data), replace = TRUE), ]
  

# Fit the CFA model
fit <- cfa(cfa_model, data = bootstrap_sample,std.lv=TRUE, auto.efa = TRUE, estimator = "WLSMV")

 # Calculate reliability metrics (including Composite Reliability)
reliability_metrics <- semTools::reliability(fit)
  CR<-reliability_metrics[2,]
 AVE<-reliability_metrics[5,]
  

  # Extract relevant fit measures
  fit_measures <- fitMeasures(fit, c("chisq.scaled", "srmr", "tli.scaled", "cfi.scaled", "rmsea.scaled"))

  fit_measures<-c(fit_measures, CR, AVE)
 
  return(fit_measures)
}

# Perform bootstrap sampling
set.seed(123)  # For reproducibility

# Initialize matrix to store CR, Omega, and AVE
fit_metrics <- matrix(NA, nrow = num_bootstrap, ncol = 17)
# List of columns to calculate confidence intervals for
columns_to_ci <- c("chisq.scaled", "srmr", "tli.scaled", "cfi.scaled", "rmsea.scaled", 
                   "CR.Achiever", "CR.Disruptor", "CR.FreeSpirit", "CR.Philanthropist", 
                   "CR.Player", "CR.Socializer", 
                   "AVE.Achiever", "AVE.Disruptor", "AVE.FreeSpirit", 
                   "AVE.Philanthropist", "AVE.Player", "AVE.Socializer")
colnames(fit_metrics) <- columns_to_ci

# Bootstrap loop
for (i in 1:num_bootstrap) {
  fit_metrics[i, ] <- bootstrap_cfa_cr_omega_ave(hexad_data_52, cfa_model)
}
dim(hexad_data_52)


  names(fit_measures_final) <- columns_to_ci
  #summary(fit, fit.measures = TRUE, standardized = TRUE, rsquare = TRUE)
  

# Initialize an empty data frame to store the results
results_table_52 <- data.frame(
  Metric = columns_to_ci,
  Estimate = numeric(length(columns_to_ci)),
  CI_Lower = numeric(length(columns_to_ci)),
  CI_Upper = numeric(length(columns_to_ci)),
  stringsAsFactors = FALSE
)

# Populate the results table with confidence intervals and estimates
for (i in seq_along(columns_to_ci)) {
  col <- columns_to_ci[i]
  ci <- quantile(fit_metrics[, col], probs = c(0.025, 0.975))
  results_table_52$Estimate[i] <- round(fit_measures_final[col], 3)  # Add the estimate and round
  results_table_52$CI_Lower[i] <- round(ci[1], 3)  # Round lower CI
  results_table_52$CI_Upper[i] <- round(ci[2], 3)  # Round upper CI
}


# Correctly print the table in a nicely formatted way
results_table_52[1:5,] %>%
  kbl(caption = "CFA  metrics with confident interval", format = "markdown",digits  = 3) %>%
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover", "condensed", "responsive"))


```

#### Appendix A13. Standardized Residuals for the Hexad-12 items from the CFA

```{r}
# Local Fit: Residuals  Standardized residuals
standardized_residuals <- residuals(fit, type = "standardized")


kable(standardized_residuals, caption = "Standardized Residuals for the Hexad-12 items from the CFA",digits  = 3)

```

#### Appendix A14. Correlation Residuals for the Hexad-12 items from the CFA

```{r}
#Correlation residuals


kable(residuals(fit, type = "cor"), caption = "Correlation Residuals for the Hexad-12 items from the CFA",digits  = 3)

```

#### Appendix A15. Modification indices Hexad-12 scale

```{r}


# Extract all modification indices, sorted from highest to lowest
mi <- modindices(fit, sort. = TRUE)

# Show the top 20 largest MIs for inspection
table_MI<-mi[,c(1:5,7)]
colnames(table_MI)<-c("Path", "", "", "MI", "EPC", "Std.EPC")


kable(head(table_MI, 10), caption = " Modification indices Hexad-12 scale",digits  = 3)

```

## 4.3. Score Reliability

#### Table 7: Reliability metrics

```{r, cache=TRUE}


set.seed(123)


subscale_pairs <- list(
  Philanthropist = c("P1", "P4"),
  Socializer     = c("S2", "S4"),
  Achiever       = c("A2", "A4"),
  Player         = c("R2", "R4"),
  Disruptor      = c("D3", "D4"),
  `Free Spirit`  = c("F1", "F3")
)

# Coerce characters to numeric once
for (nm in unique(unlist(subscale_pairs))) {
  if (is.character(merged_hexad[[nm]])) merged_hexad[[nm]] <- as.integer(merged_hexad[[nm]])
}


safe_boot_ci <- function(boot_obj, probs = c(0.025, 0.975)) {
  x <- boot_obj$t
  x <- x[is.finite(x)]
  if (length(x) < 50) return(c(NA, NA))
  quantile(x, probs = probs, na.rm = TRUE)
}

# Spearman–Brown
spearman_brown_fn <- function(data, indices, item1, item2) {
  samp <- data[indices, c(item1, item2)]
  r <- suppressWarnings(cor(samp[[item1]], samp[[item2]], method = "pearson",
                            use = "pairwise.complete.obs"))
  2*r/(1+r)
}

# McDonald's omega
mcdonald_omega_fn <- function(data, indices, item1, item2) {
  samp <- data[indices, c(item1, item2)]
  suppressWarnings(psych::omega(samp, nfactors = 1, plot = FALSE)$omega.tot)
}

# Ordinal omega (polychoric)
ordinal_omega_psych_fn <- function(data, indices, item1, item2) {
  samp <- data[indices, c(item1, item2)]
  # ordered factors
  samp[[item1]] <- ordered(samp[[item1]])
  samp[[item2]] <- ordered(samp[[item2]])
  out <- try(psych::omega(samp, nfactors=1, plot=FALSE, poly=TRUE)$omega.tot,
             silent = TRUE)
  if (inherits(out, "try-error")) return(NA) else out
}

# Ordinal Composite Reliability via WLSMV CFA
ordinal_cr_twoitem <- function(data, indices, item1, item2) {
  samp <- data[indices, c(item1, item2)]

  # enforce ordered factors
  lvls <- sort(unique(na.omit(c(samp[[item1]], samp[[item2]]))))
  if (all(lvls %in% 1:7)) lvls <- 1:7
  samp[[item1]] <- factor(samp[[item1]], levels = lvls, ordered = TRUE)
  samp[[item2]] <- factor(samp[[item2]], levels = lvls, ordered = TRUE)

  mdl <- paste0("f =~ ", item1, " + ", item2)

  fit <- try(
    lavaan::cfa(mdl, data = samp, ordered = c(item1, item2),
                estimator = "WLSMV", std.lv = TRUE),
    silent = TRUE
  )
  if (inherits(fit, "try-error")) return(NA)

  ss <- standardizedSolution(fit)
  lam <- ss[ss$op == "=~" & ss$lhs == "f", "est.std"]
  the <- ss[ss$op == "~~" & ss$lhs == ss$rhs, "est.std"]

  num <- (sum(lam))^2
  den <- num + sum(the)
  num/den
}


R_boot <- num_bootstrap  # user-defined earlier

final_results <- list()

for (sb in names(subscale_pairs)) {
  item1 <- subscale_pairs[[sb]][1]
  item2 <- subscale_pairs[[sb]][2]

  # ----- Spearman-Brown -----
  sb_boot <- boot(merged_hexad, statistic = spearman_brown_fn,
                  R = R_boot, item1 = item1, item2 = item2)
  sb_est <- sb_boot$t0
  sb_ci  <- safe_boot_ci(sb_boot)

  # ----- McDonald's omega -----
  om_boot <- boot(merged_hexad, statistic = mcdonald_omega_fn,
                  R = R_boot, item1 = item1, item2 = item2)
  om_est <- om_boot$t0
  om_ci  <- safe_boot_ci(om_boot)

  # ----- Ordinal omega -----
  oo_boot <- boot(merged_hexad, statistic = ordinal_omega_psych_fn,
                  R = R_boot, item1 = item1, item2 = item2)
  oo_est <- oo_boot$t0
  oo_ci  <- safe_boot_ci(oo_boot)


  final_results[[sb]] <- tibble(
    Subscale = sb,
    SB_Estimate = round(sb_est, 2),
    SB_CI_Lower = round(sb_ci[1], 2),
    SB_CI_Upper = round(sb_ci[2], 2),

    Omega_Estimate = round(om_est, 2),
    Omega_CI_Lower = round(om_ci[1], 2),
    Omega_CI_Upper = round(om_ci[2], 2),

    OrdOmega_Estimate = round(oo_est, 2),
    OrdOmega_CI_Lower = round(oo_ci[1], 2),
    OrdOmega_CI_Upper = round(oo_ci[2], 2),

  )
}


final_table <- bind_rows(final_results)

kable(t(as.matrix(final_table)), caption = " Reliability Table for  Hexad-12 Subscales", digits = 3)

```

```{r}


set.seed(123)

subscale_items <- list(
  "Philanthropist" = c("P1", "P4"),
  "Socializer"     = c("S2", "S4"),
  "Achiever"       = c("A2", "A4"),
  "Player"         = c("R2", "R4"),
  "Disruptor"      = c("D3", "D4"),
  "Free Spirit"    = c("F1", "F3")
)

# If some items are stored as character, coerce once to integers
for (nm in unique(unlist(subscale_items))) {
  if (is.character(merged_hexad[[nm]])) merged_hexad[[nm]] <- as.integer(merged_hexad[[nm]])
}

safe_boot_ci <- function(x, probs = c(0.025, 0.975)) {
  x <- x[is.finite(x)]
  if (length(x) < 50) return(c(NA_real_, NA_real_))  # too few valid draws
  as.numeric(quantile(x, probs = probs, na.rm = TRUE, names = FALSE))
}

# --------- Ordinal CR for a TWO-ITEM subscale via ordinal CFA ----------
# CR = (sum(lambda))^2 / ((sum(lambda))^2 + sum(theta)),
# where lambda, theta are from the STANDARDIZED solution of a WLSMV CFA with ordered indicators.
ordinal_cr_twoitem <- function(data, indices, item1, item2) {
  samp <- data[indices, c(item1, item2)]

  # Guard against degenerate resamples (need >= 2 categories in each item)
  if (length(unique(na.omit(samp[[item1]]))) < 2 ||
      length(unique(na.omit(samp[[item2]]))) < 2) return(NA_real_)

  # Make ordered factors (preserve 1:7 if applicable)
  all_lvls <- sort(unique(na.omit(c(samp[[item1]], samp[[item2]]))))
  if (all(all_lvls %in% 1:7)) all_lvls <- 1:7
  samp[[item1]] <- factor(samp[[item1]], levels = all_lvls, ordered = TRUE)
  samp[[item2]] <- factor(samp[[item2]], levels = all_lvls, ordered = TRUE)

  mdl <- paste0("f =~ ", item1, " + ", item2)

  fit <- try(
    lavaan::cfa(
      mdl,
      data      = samp,
      ordered   = c(item1, item2),
      estimator = "WLSMV",
      std.lv    = TRUE,
      warn      = FALSE
    ),
    silent = TRUE
  )
  if (inherits(fit, "try-error")) return(NA_real_)

  # Extract standardized loadings and residual variances
  ss <- try(lavaan::standardizedSolution(fit), silent = TRUE)
  if (inherits(ss, "try-error")) return(NA_real_)

  lam <- ss[ss$op == "=~" & ss$lhs == "f" & ss$rhs %in% c(item1, item2), "est.std"]
  the <- ss[ss$op == "~~" & ss$lhs == ss$rhs & ss$lhs %in% c(item1, item2), "est.std"]

  if (length(lam) != 2L || length(the) != 2L) return(NA_real_)
  if (!all(is.finite(lam)) || !all(is.finite(the))) return(NA_real_)

  num <- (sum(lam))^2
  den <- num + sum(the)
  cr  <- num / den
  as.numeric(cr)
}

# --------- Compute Ordinal CR + 95% CI for each subscale ----------
  # reduce to 5000 for speed if needed

ordCR_est <- c(); ordCR_ciL <- c(); ordCR_ciU <- c()

for (sb in names(subscale_items)) {
  it <- subscale_items[[sb]]
  b <- boot(
    data      = merged_hexad,
    statistic = ordinal_cr_twoitem,
    R         = R_boot,
    item1     = it[1],
    item2     = it[2]
  )
  ordCR_est[sb] <- b$t0
  ci <- safe_boot_ci(b$t)
  ordCR_ciL[sb] <- ci[1]; ordCR_ciU[sb] <- ci[2]
}

# --------- Results as a tidy data frame ----------
ordinal_cr_results <- data.frame(
  Subscale = names(subscale_items),
  OrdCR_Estimate   = round(ordCR_est, 2),
  OrdCR_CI_Lower   = round(ordCR_ciL, 2),
  OrdCR_CI_Upper   = round(ordCR_ciU, 2),
  row.names = NULL,
  check.names = FALSE
)


kable(ordinal_cr_results, caption = " Ordinal CR for  Hexad-12 Subscales", digits = 3)


```

## 4.4.Internal-Structure Evidence

#### Appendix A16. Heterotrait–Monotrait (HTMT) ratios

```{r, cache=TRUE}


set.seed(123)
hexad_data<-data

stopifnot(exists("hexad_data"))

ord_items <- c("A2","A4","D3","D4","F1","F3","P1","P4","R2","R4","S2","S4")

# Coerce to integer if needed
for (v in ord_items) if (is.character(hexad_data[[v]])) hexad_data[[v]] <- as.integer(hexad_data[[v]])

# Items per factor (labels used in tables)
blocks <- list(
  Philanthropist = c("P1","P4"),
  Socializer     = c("S2","S4"),
  FreeSpirit     = c("F1","F3"),
  Achiever       = c("A2","A4"),
  Player         = c("R2","R4"),
  Disruptor      = c("D3","D4")
)
fac_names <- names(blocks)

#--------------------------- CFA (ordinal WLSMV) ---------------------------
cfa_model <- '
  Achiever       =~ A2 + A4
  Disruptor      =~ D3 + D4
  FreeSpirit     =~ F1 + F3
  Philanthropist =~ P1 + P4
  Player         =~ R2 + R4
  Socializer     =~ S2 + S4
'
fit_wlsmv <- cfa(
  cfa_model,
  data             = hexad_data,
  estimator        = "WLSMV",
  ordered          = ord_items,
  parameterization = "theta",
  std.lv           = TRUE
)


htmt_from_R <- function(R, blocks) {
  f <- length(blocks)
  out <- matrix(NA_real_, f, f, dimnames = list(names(blocks), names(blocks)))

  # within-construct mean |r|
  within <- vapply(blocks, function(items) {
    if (length(items) < 2) return(NA_real_)
    idx <- combn(items, 2, simplify = FALSE)
    mean(abs(vapply(idx, function(p) R[p[1], p[2]], 0.0)), na.rm = TRUE)
  }, 0.0)

  for (i in seq_len(f-1)) {
    for (j in (i+1):f) {
      a <- blocks[[i]]; b <- blocks[[j]]
      num <- mean(as.vector(abs(R[a, b, drop = FALSE])), na.rm = TRUE)
      den <- sqrt(within[i] * within[j])
      out[i, j] <- num / den
      out[j, i] <- out[i, j]
    }
  }
  out
}

# Bootstrap CI helpers (scalar outputs)
get_ci <- function(x) {
  x <- x[is.finite(x)]
  if (length(x) < 50) return(c(NA_real_, NA_real_))
  as.numeric(stats::quantile(x, c(0.025, 0.975), na.rm = TRUE, names = FALSE))
}
get_ci_lower <- function(x) get_ci(x)[1]
get_ci_upper <- function(x) get_ci(x)[2]

use_semtools <- FALSE
HTMT_mat <- NULL

if (requireNamespace("semTools", quietly = TRUE)) {
  # Older semTools::htmt() often has no 'type' arg; try plain call.
  try({
    HTMT_mat <- semTools::htmt(fit_wlsmv)
    use_semtools <- TRUE
  }, silent = TRUE)
}

if (!use_semtools || is.null(HTMT_mat)) {
  message("Falling back to manual HTMT using polychoric correlations (lavaan::lavCor).")
  R_poly <- lavaan::lavCor(
    hexad_data[, ord_items, drop = FALSE],
    ordered   = ord_items,
    estimator = "WLSMV"
  )
  R_poly <- R_poly[ord_items, ord_items]
  HTMT_mat <- htmt_from_R(R_poly, blocks)
}

HTMT_max <- max(HTMT_mat[upper.tri(HTMT_mat)], na.rm = TRUE)
cat("\nMaximum HTMT:", round(HTMT_max, 3),
    " | Strict OK (< .85)?", HTMT_max < .85,
    " | Lenient OK (< .90)?", HTMT_max < .90, "\n\n")


R_boot <- num_bootstrap   
HTMT_cube <- array(NA_real_, dim = c(length(blocks), length(blocks), R_boot),
                   dimnames = list(fac_names, fac_names, NULL))

boot_ids <- replicate(R_boot, sample(seq_len(nrow(hexad_data)), replace = TRUE), simplify = FALSE)

for (b in seq_len(R_boot)) {
  samp <- hexad_data[boot_ids[[b]], ord_items, drop = FALSE]
  Rb <- try(lavaan::lavCor(samp, ordered = ord_items, estimator = "WLSMV"), silent = TRUE)
  if (inherits(Rb, "try-error")) next
  Rb <- Rb[ord_items, ord_items]
  HTMT_b <- htmt_from_R(Rb, blocks)
  HTMT_cube[, , b] <- HTMT_b
}

# Upper-triangle pairs table with scalar CI columns
pairs <- as.data.frame(t(combn(fac_names, 2)), stringsAsFactors = FALSE)
colnames(pairs) <- c("Factor1","Factor2")

appendix_tbl <- pairs %>%
  rowwise() %>%
  mutate(
    HTMT     = HTMT_mat[Factor1, Factor2],
    CI_lower = get_ci_lower(HTMT_cube[Factor1, Factor2, ]),
    CI_upper = get_ci_upper(HTMT_cube[Factor1, Factor2, ]),
    Strict_OK  = HTMT < .85,
    Lenient_OK = HTMT < .90
  ) %>%
  ungroup() %>%
  mutate(
    HTMT     = round(HTMT, 3),
    CI_lower = round(CI_lower, 3),
    CI_upper = round(CI_upper, 3)
  )

print(knitr::kable(
  appendix_tbl[, c(1:5)],
  caption = paste0("HTMT (polychoric) with 95% bootstrap CIs; max HTMT = ",
                   round(HTMT_max, 3),
                   "  [R_boot = ", R_boot, "]")
))



```

#### Table 8: Bivariate correlation coefficients Kendall's tau between the Hexad subscales

```{r}

# Reorganize columns in the desired order
columns <- c("philanthropist", "socializer", "achiever", "player", "disruptor", "freeSpirit")
data_subset <- data[columns]

# Initialize matrices for correlations and p-values
n <- length(columns)
cor_matrix <- matrix("", n, n, dimnames = list(columns, columns))
p_matrix <- matrix(NA, n, n, dimnames = list(columns, columns))

# Calculate Kendall Tau correlations and p-values
for (i in 1:n) {
  for (j in i:n) {
    if (i == j) {
      cor_matrix[i, j] <- "1.000"
    } else {
      test <- cor.test(data_subset[[i]], data_subset[[j]], method = "kendall", use = "pairwise.complete.obs")
      correlation <- round(test$estimate, 3)
      p_value <- round(test$p.value, 3)
      significance <- ifelse(p_value < 0.001, "***", 
                      ifelse(p_value < 0.01, "**", 
                      ifelse(p_value < 0.05, "*", "")))
      
      cor_matrix[i, j] <- ""
      cor_matrix[j, i] <- paste0(correlation, significance)
    }
  }
}

# Convert the correlation matrix to a data frame for display
cor_matrix_df <- as.data.frame(cor_matrix, row.names = columns)
rownames(cor_matrix_df) <- c("Philanthropist", "Socializer", "Achiever", "Player", "Disruptor", "Free Spirit")
colnames(cor_matrix_df) <- c("Philanthropist", "Socializer", "Achiever", "Player", "Disruptor", "Free Spirit")

# Display the correlation matrix as a nicely formatted RMarkdown table
cor_matrix_df %>%
  kbl(
    caption = "Lower Triangle of Kendall Tau Correlation Matrix with Significance. Significance Legend: *** p < 0.001, ** p < 0.01, * p < 0.05"
  ) %>%
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```

#### Appendix A17. Latent correlations among Hexad determinants

```{r}
# ------------------------------------------------------------
# Appendix A17: Latent correlations among Hexad determinants
# Corrected version using standardizedSolution()
# ------------------------------------------------------------

library(lavaan)
library(dplyr)
library(knitr)
library(kableExtra)

# Use the final analytical dataset
# Change this line only if your final dataset object has a different name
analysis_data <- hexad_data

# Item columns
item_cols <- c(
  "A2", "A4",
  "D3", "D4",
  "F1", "F3",
  "P1", "P4",
  "R2", "R4",
  "S2", "S4"
)

# CFA model
cfa_model <- '
  Achiever       =~ A2 + A4
  Disruptor      =~ D3 + D4
  FreeSpirit     =~ F1 + F3
  Philanthropist =~ P1 + P4
  Player         =~ R2 + R4
  Socializer     =~ S2 + S4
'

# Always refit a fresh model for this table.
# Do not reuse an existing object called "fit".
fit_latcor <- lavaan::cfa(
  cfa_model,
  data = analysis_data,
  std.lv = TRUE,
  estimator = "WLSMV",
  ordered = item_cols
)

# Desired reporting order
desired_order <- c(
  "Philanthropist",
  "Socializer",
  "FreeSpirit",
  "Achiever",
  "Player",
  "Disruptor"
)

# Extract standardized solution with standardized confidence intervals
std_sol <- lavaan::standardizedSolution(
  fit_latcor,
  ci = TRUE
)

# Keep only latent-factor correlations
lat_ci <- std_sol %>%
  filter(
    op == "~~",
    lhs != rhs,
    lhs %in% desired_order,
    rhs %in% desired_order
  ) %>%
  mutate(
    lhs_order = match(lhs, desired_order),
    rhs_order = match(rhs, desired_order)
  ) %>%
  arrange(lhs_order, rhs_order) %>%
  transmute(
    `Factor 1` = lhs,
    `Factor 2` = rhs,
    `Latent r` = est.std,
    `95% CI Lower` = ci.lower,
    `95% CI Upper` = ci.upper
  )

# Print table
lat_ci %>%
  kable(
    caption = "Latent correlations among Hexad determinants",
    digits = 3,
    format = "markdown"
  ) %>%
  kable_styling(
    full_width = FALSE,
    bootstrap_options = c("striped", "hover", "condensed", "responsive")
  )
```

## 4.5. External Relations and Group Analyses

### Game frequency-related patterns in Hexad-12 scores.

#### Appendix A18. Correlations between Hexad determinants and gaming frequency

```{r}


data_hexad <- data    

freq_var <- "Freq.Games"

hexad_cols <- c("philanthropist", "socializer", "freeSpirit",
                "achiever", "player", "disruptor")

# 1. Clean frequency input
hexad_clean <- data_hexad %>%
  mutate(
    Freq_raw = trimws(as.character(.data[[freq_var]])),
    Freq     = suppressWarnings(as.numeric(Freq_raw))
  ) %>%
  filter(!is.na(Freq))

total_n <- nrow(hexad_clean)

# 2. Retain only determinant columns that exist and coerce to numeric
present_hexad <- intersect(hexad_cols, names(hexad_clean))

for (v in present_hexad) {
  hexad_clean[[v]] <- suppressWarnings(as.numeric(as.character(hexad_clean[[v]])))
}

# 3. Loop correlations and bind into one table
results_df <- lapply(present_hexad, function(var_name) {
  
  ct <- suppressWarnings(
    cor.test(hexad_clean$Freq,
             hexad_clean[[var_name]],
             method = "kendall", 
             exact = FALSE)
  )
  
  data.frame(
    Determinant = var_name,
    n           = total_n,
    tau         = unname(ct$estimate),
    p_value     = ct$p.value,
    stringsAsFactors = FALSE
  )
}) %>% bind_rows()

# 4. Print table
kable(results_df,
      caption = "Correlations between Hexad determinants and gaming frequency",
      digits = 3)

```

#### Appendix A19. Kruskal–Wallis test for Hexad determinants by gaming frequency

```{r}
library(dplyr)
library(tidyr)



data_hexad <- data       #

freq_var <- "Freq.Games"       # game-frequency variable

hexad_cols <- c("philanthropist", "socializer", "freeSpirit",
                "achiever", "player", "disruptor")


hexad_clean <- data_hexad %>%
  mutate(
    Freq_raw = trimws(as.character(.data[[freq_var]])),
    Freq     = suppressWarnings(as.numeric(Freq_raw))
  ) %>%
  filter(!is.na(Freq))

present_hexad_cols <- intersect(hexad_cols, names(hexad_clean))

hexad_clean <- hexad_clean %>%
  mutate(across(
    all_of(present_hexad_cols),
    ~ suppressWarnings(as.numeric(as.character(.x)))
  ))



# (a) total sample size per frequency
n_by_freq <- hexad_clean %>%
  count(Freq, name = "n_total") %>%
  arrange(Freq)


# sum(n_by_freq$n_total) should be 648




hexad_grouped <- hexad_clean %>%
  mutate(
    FreqGroup = case_when(
      Freq %in% 1:2 ~ "1--2 days",
      Freq %in% 3:4 ~ "3--4 days",
      Freq %in% 5:7 ~ "5--7 days",
      TRUE          ~ NA_character_
    )
  ) %>%
  filter(!is.na(FreqGroup))

# sample size per group
n_by_group <- hexad_grouped %>%
  count(FreqGroup, name = "n_total") %>%
  arrange(match(FreqGroup, c("1--2 days", "3--4 days", "5--7 days")))


# Kruskal-Wallis tests, Bonferroni-adjusted p-values,
# and epsilon-squared effect sizes
kw_results <- hexad_grouped %>%
  pivot_longer(
    cols = all_of(present_hexad_cols),
    names_to = "Determinant",
    values_to = "Score"
  ) %>%
  filter(!is.na(Score)) %>%
  group_by(Determinant) %>%
  summarise(
    n_total = n(),
    n_groups = n_distinct(FreqGroup),
    test_res = list(kruskal.test(Score ~ FreqGroup)),
    .groups = "drop"
  ) %>%
  mutate(
    statistic = map_dbl(test_res, ~ unname(.x$statistic)),
    df = map_dbl(test_res, ~ unname(.x$parameter)),
    p_value = map_dbl(test_res, ~ .x$p.value),

    # Bonferroni correction across the six Hexad comparisons
    p_adj_bonferroni = p.adjust(
      p_value,
      method = "bonferroni"
    ),

    # Kruskal-Wallis epsilon-squared:
    # epsilon^2 = (H - k + 1) / (n - k)
    epsilon_sq = (
      statistic - n_groups + 1
    ) / (
      n_total - n_groups
    ),

    # Set negative estimates to zero
    epsilon_sq = pmax(0, epsilon_sq)
  ) %>%
  dplyr::select(
    Determinant,
    n_total,
    statistic,
    df,
    p_value,
    p_adj_bonferroni,
    epsilon_sq
  ) %>%
  arrange(Determinant)

# Format values for presentation
kw_formatted <- kw_results %>%
  mutate(
    statistic = round(statistic, 2),
    df = as.integer(df),
    p_value = round(p_value, 3),
    p_adj_bonferroni = round(p_adj_bonferroni, 3),
    epsilon_sq = round(epsilon_sq, 3)
  )

# Updated Appendix A19 table
kable(
  kw_formatted,
  caption = paste(
    "Kruskal--Wallis tests, Bonferroni-adjusted p-values,",
    "and epsilon-squared effect sizes for Hexad determinants",
    "by gaming frequency"
  ),
  col.names = c(
    "Determinant",
    "n",
    "Kruskal--Wallis",
    "Degrees of Freedom",
    "p-value",
    "Adj. p-value",
    "Epsilon-squared"
  ),
  align = c("l", "r", "r", "r", "r", "r", "r")
)
```



#### Multigroup confirmatory factor analysis

```{r}

data_cfa <- merged_hexad


hexad_items <- c("A2","A4",
                 "D3","D4",
                 "F1","F3",
                 "P1","P4",
                 "R2","R4",
                 "S2","S4")


freq <- data_cfa$Freq.Games   

data_cfa$Freq3 <- NA_character_
data_cfa$Freq3[freq %in% c(1,2)] <- "1-2 days"
data_cfa$Freq3[freq %in% c(3,4)] <- "3-4 days"
data_cfa$Freq3[freq %in% c(5,6,7)] <- "5-7 days"

data_cfa$Freq3 <- factor(data_cfa$Freq3,
                         levels = c("1-2 days","3-4 days","5-7 days"))

table(data_cfa$Freq3, useNA = "ifany")


data_mi <- data_cfa[, c("Freq3", hexad_items)]
data_mi <- data_mi[!is.na(data_mi$Freq3), ]
data_mi <- data_mi[complete.cases(data_mi[, hexad_items]), ]

# convert items to numeric continuous
for (v in hexad_items) data_mi[[v]] <- as.numeric(data_mi[[v]])

table(data_mi$Freq3)
nrow(data_mi)

hexad_model <- '
  Achiever       =~ A2 + A4
  Disruptor      =~ D3 + D4
  FreeSpirit     =~ F1 + F3
  Philanthropist =~ P1 + P4
  Player         =~ R2 + R4
  Socializer     =~ S2 + S4
'


fit_config <- cfa(
  hexad_model,
  data      = data_mi,
  group     = "Freq3",
  estimator = "MLR"
)


fit_metric <- cfa(
  hexad_model,
  data        = data_mi,
  group       = "Freq3",
  group.equal = c("loadings"),
  estimator   = "MLR"
)


fit_scalar <- cfa(
  hexad_model,
  data        = data_mi,
  group       = "Freq3",
  group.equal = c("loadings","intercepts"),
  estimator   = "MLR"
)


anova_results <- anova(fit_config, fit_metric, fit_scalar)
anova_results


get_fits <- function(fit) {
  fitMeasures(fit, c("cfi","rmsea","srmr"))
}

fit_table <- rbind(
  config = round(get_fits(fit_config),3),
  metric = round(get_fits(fit_metric),3),
  scalar = round(get_fits(fit_scalar),3)
)

fit_table


```

### Gender-related patterns in Hexad-12 scores.

#### Appendix A20. Kruskal–Wallis test for Hexad determinants by Gender


```{r}

library(dplyr)
library(knitr)

hexad_vars <- c(
  "philanthropist",
  "socializer",
  "freeSpirit",
  "achiever",
  "player",
  "disruptor"
)

# Keep rows with non-missing gender
data_gender <- merged_hexad %>%
  filter(!is.na(Gender))

# Run Kruskal-Wallis tests for each determinant
results_list <- lapply(hexad_vars, function(var_name) {

  # Create a temporary data frame and remove missing scores
  df_sub <- data.frame(
    gender = data_gender$Gender,
    score = suppressWarnings(
      as.numeric(as.character(data_gender[[var_name]]))
    )
  ) %>%
    filter(
      !is.na(gender),
      !is.na(score)
    )

  # Valid sample size and number of gender groups
  n_total <- nrow(df_sub)
  n_groups <- n_distinct(df_sub$gender)

  # Return missing results if the test cannot be conducted
  if (n_groups < 2 || n_total <= n_groups) {
    return(
      data.frame(
        Determinant = var_name,
        n = n_total,
        statistic = NA_real_,
        df = NA_real_,
        p_value = NA_real_,
        epsilon_sq = NA_real_
      )
    )
  }

  # Run the Kruskal-Wallis test
  kt <- kruskal.test(score ~ gender, data = df_sub)

  # Extract the Kruskal-Wallis H statistic
  H <- unname(kt$statistic)

  # Kruskal-Wallis epsilon-squared:
  # epsilon^2 = (H - k + 1) / (n - k)
  epsilon_sq <- (
    H - n_groups + 1
  ) / (
    n_total - n_groups
  )

  # Negative estimates may occur because of sampling variation
  epsilon_sq <- max(0, epsilon_sq)

  # Return unrounded results
  data.frame(
    Determinant = var_name,
    n = n_total,
    statistic = H,
    df = unname(kt$parameter),
    p_value = kt$p.value,
    epsilon_sq = epsilon_sq
  )
})

# Combine results
kw_results <- bind_rows(results_list) %>%

  # Apply Bonferroni correction across the six determinant tests
  mutate(
    p_adj_bonferroni = p.adjust(
      p_value,
      method = "bonferroni"
    )
  ) %>%

  # Arrange determinants in the desired table order
  mutate(
    Determinant = factor(
      Determinant,
      levels = hexad_vars,
      labels = c(
        "Philanthropist",
        "Socializer",
        "Free Spirit",
        "Achiever",
        "Player",
        "Disruptor"
      )
    )
  ) %>%
  arrange(Determinant) %>%

  # Select columns in the same order as Table A19
  dplyr::select(
    Determinant,
    n,
    statistic,
    df,
    p_value,
    p_adj_bonferroni,
    epsilon_sq
  )

# Format values only after calculating adjusted p-values
kw_formatted <- kw_results %>%
  mutate(
    statistic = round(statistic, 2),
    df = as.integer(df),
    p_value = round(p_value, 3),
    p_adj_bonferroni = round(p_adj_bonferroni, 3),
    epsilon_sq = round(epsilon_sq, 3)
  )

# Updated Appendix A20 table
kable(
  kw_formatted,
  caption = paste(
    "Kruskal-Wallis tests, Bonferroni-adjusted p-values,",
    "and epsilon-squared effect sizes for Hexad determinants",
    "by gender"
  ),
  col.names = c(
    "Determinant",
    "n",
    "Kruskal-Wallis",
    "d.f.",
    "p-value",
    "adj. p-value",
    "Epsilon-squared"
  ),
  align = c("l", "r", "r", "r", "r", "r", "r")
)

```

#### Multigroup Confirmatory factor Analysis

```{r  b4}

data_cfa <- merged_hexad   


hexad_items <- c("A2","A4",
                 "D3","D4",
                 "F1","F3",
                 "P1","P4",
                 "R2","R4",
                 "S2","S4")

data_cfa$Gender2 <- NA_character_

data_cfa$Gender2[data_cfa$Gender %in% c("female")] <- "Female"
data_cfa$Gender2[data_cfa$Gender %in% c("male")] <- "Male"

# Factor with correct order
data_cfa$Gender2 <- factor(data_cfa$Gender2, levels = c("Female","Male"))


# Keep only Gender2 + items
data_mi <- data_cfa[, c("Gender2", hexad_items)]

# Remove rows with missing Gender2
data_mi <- data_mi[!is.na(data_mi$Gender2), ]

# Remove rows with missing any Hexad item
data_mi <- data_mi[complete.cases(data_mi[, hexad_items]), ]

# Convert items to numeric continuous
for (v in hexad_items) {
  data_mi[[v]] <- as.numeric(data_mi[[v]])
}

## Check sample size for each group
table(data_mi$Gender2)
nrow(data_mi)

hexad_model <- '
  Achiever       =~ A2 + A4
  Disruptor      =~ D3 + D4
  FreeSpirit     =~ F1 + F3
  Philanthropist =~ P1 + P4
  Player         =~ R2 + R4
  Socializer     =~ S2 + S4
'


fit_overall <- cfa(
  hexad_model,
  data      = data_mi,
  estimator = "MLR"
)

#summary(fit_overall, fit.measures = TRUE, standardized = TRUE)


fit_config <- cfa(
  hexad_model,
  data      = data_mi,
  group     = "Gender2",
  estimator = "MLR"
)


fit_metric <- cfa(
  hexad_model,
  data        = data_mi,
  group       = "Gender2",
  group.equal = c("loadings"),
  estimator   = "MLR"
)


fit_scalar <- cfa(
  hexad_model,
  data        = data_mi,
  group       = "Gender2",
  group.equal = c("loadings","intercepts"),
  estimator   = "MLR"
)


anova_results <- anova(fit_config, fit_metric, fit_scalar)
anova_results


get_fits <- function(fit) {
  fitMeasures(fit, c("cfi", "rmsea", "srmr"))
}

fit_table <- rbind(
  config = round(get_fits(fit_config),3),
  metric = round(get_fits(fit_metric),3),
  scalar = round(get_fits(fit_scalar),3)
)

fit_table

```

### Age-related patterns in Hexad-12 scores.

#### Appendix A21. Correlations between Hexad determinants and Age

```{r  b5}


# Hexad determinant column names in merged_hexad
hexad_dets <- c(
  "philanthropist", "socializer", "freeSpirit",
  "achiever", "player", "disruptor"
)


merged_hexad_age <- merged_hexad %>%
  filter(!is.na(Age)) %>%
  mutate(
    AgeGroup = case_when(
      Age >= 18 & Age <= 24 ~ "18–24",
      Age >= 25 & Age <= 34 ~ "25–34",
      Age >= 35 & Age <= 49 ~ "35–49",
      Age >= 50             ~ "50+",
      TRUE ~ NA_character_
    ),
    AgeGroup = factor(AgeGroup, levels = c("18–24", "25–34", "35–49", "50+"))
  )


age_kendall <- hexad_dets %>%
  map_df(function(det) {
    x <- merged_hexad_age$Age
    y <- merged_hexad_age[[det]]
    idx <- !is.na(x) & !is.na(y)

    kt <- cor.test(x[idx], y[idx], method = "kendall", exact = FALSE)

    tibble(
      Determinant = det,
      n = sum(idx),
      tau = unname(kt$estimate),
      p_value = kt$p.value
    )
  }) %>%
  mutate(
    p_adj_bonferroni = p.adjust(p_value, method = "bonferroni"),
    tau = round(tau, 3),
    p_value = round(p_value, 3),
    p_adj_bonferroni = round(p_adj_bonferroni, 3)
  )


kable(age_kendall[,-5], caption = "Correlations between Hexad determinants and Age")


```

#### Appendix A22. Kruskal–Wallis test for Hexad determinants by Age Group

```{r}
library(dplyr)
library(purrr)
library(tibble)
library(knitr)

# Run Kruskal-Wallis tests for each Hexad determinant
kw_results <- hexad_dets %>%
  map_df(function(det) {

    # Retain observations with a valid age group and determinant score
    df_sub <- merged_hexad_age %>%
      transmute(
        AgeGroup = AgeGroup,
        Score = suppressWarnings(
          as.numeric(as.character(.data[[det]]))
        )
      ) %>%
      filter(
        !is.na(AgeGroup),
        !is.na(Score)
      )

    # Determine the valid sample size and number of age groups
    n_total <- nrow(df_sub)
    n_groups <- n_distinct(df_sub$AgeGroup)

    # Return missing results if the test cannot be conducted
    if (n_groups < 2 || n_total <= n_groups) {
      return(
        tibble(
          Determinant = det,
          n = n_total,
          statistic = NA_real_,
          df = NA_real_,
          p_value = NA_real_,
          epsilon_sq = NA_real_
        )
      )
    }

    # Run the Kruskal-Wallis test
    kw <- kruskal.test(
      Score ~ AgeGroup,
      data = df_sub
    )

    # Extract the Kruskal-Wallis H statistic
    H <- unname(kw$statistic)

    # Kruskal-Wallis epsilon-squared:
    # epsilon^2 = (H - k + 1) / (n - k)
    epsilon_sq <- (
      H - n_groups + 1
    ) / (
      n_total - n_groups
    )

    # Negative estimates may occur because of sampling variation
    epsilon_sq <- max(0, epsilon_sq)

    # Return unrounded results
    tibble(
      Determinant = det,
      n = n_total,
      statistic = H,
      df = unname(kw$parameter),
      p_value = kw$p.value,
      epsilon_sq = epsilon_sq
    )
  }) %>%

  # Apply the Bonferroni correction across the determinant tests
  mutate(
    p_adj_bonferroni = p.adjust(
      p_value,
      method = "bonferroni"
    )
  ) %>%

  # Arrange and select columns to match Tables A19 and A20
  dplyr::select(
    Determinant,
    n,
    statistic,
    df,
    p_value,
    p_adj_bonferroni,
    epsilon_sq
  )

# Format values only after calculating adjusted p-values
kw_formatted <- kw_results %>%
  mutate(
    statistic = round(statistic, 2),
    df = as.integer(df),
    p_value = round(p_value, 3),
    p_adj_bonferroni = round(p_adj_bonferroni, 3),
    epsilon_sq = round(epsilon_sq, 3)
  )

# Updated Appendix A22 table
kable(
  kw_formatted,
  caption = paste(
    "Kruskal-Wallis tests, Bonferroni-adjusted p-values,",
    "and epsilon-squared effect sizes for Hexad determinants",
    "by age group"
  ),
  col.names = c(
    "Determinant",
    "n",
    "Kruskal-Wallis",
    "d.f.",
    "p-value",
    "Adj. p-value",
    "Epsilon-squared"
  ),
  align = c("l", "r", "r", "r", "r", "r", "r")
)

```


####  Dunn post-hoc tests with effect sizes
```{r}
library(dplyr)
library(purrr)
library(tibble)
library(stringr)
library(FSA)
library(knitr)

# Hexad determinant variables
hexad_dets <- c(
  "philanthropist",
  "socializer",
  "freeSpirit",
  "achiever",
  "player",
  "disruptor"
)

# ============================================================
# 1. Omnibus Kruskal-Wallis tests
# ============================================================

kw_results <- purrr::map_dfr(
  hexad_dets,
  function(det) {

    # Retain complete observations and convert scores to numeric
    df_sub <- merged_hexad_age %>%
      dplyr::transmute(
        AgeGroup = as.character(AgeGroup),
        Score = suppressWarnings(
          as.numeric(as.character(.data[[det]]))
        )
      ) %>%
      dplyr::filter(
        !is.na(AgeGroup),
        AgeGroup != "",
        !is.na(Score)
      )

    # Sample size and number of groups
    n_total <- nrow(df_sub)
    n_groups <- dplyr::n_distinct(df_sub$AgeGroup)

    # Return missing values if the test cannot be conducted
    if (n_groups < 2 || n_total <= n_groups) {
      return(
        tibble::tibble(
          Determinant = det,
          n = n_total,
          n_groups = n_groups,
          statistic = NA_real_,
          df = NA_real_,
          p_value = NA_real_,
          epsilon_sq = NA_real_
        )
      )
    }

    # Kruskal-Wallis test
    kw <- stats::kruskal.test(
      Score ~ AgeGroup,
      data = df_sub
    )

    H <- unname(kw$statistic)

    # Kruskal-Wallis epsilon-squared
    epsilon_sq <- (
      H - n_groups + 1
    ) / (
      n_total - n_groups
    )

    # Negative estimates may occur because of sampling variation
    epsilon_sq <- max(0, epsilon_sq)

    tibble::tibble(
      Determinant = det,
      n = n_total,
      n_groups = n_groups,
      statistic = H,
      df = unname(kw$parameter),
      p_value = kw$p.value,
      epsilon_sq = epsilon_sq
    )
  }
) %>%
  dplyr::mutate(
    # Bonferroni adjustment across the six omnibus tests
    p_adj_bonferroni = stats::p.adjust(
      p_value,
      method = "bonferroni"
    )
  ) %>%
  dplyr::select(
    Determinant,
    n,
    n_groups,
    statistic,
    df,
    p_value,
    p_adj_bonferroni,
    epsilon_sq
  )

# Display omnibus results
kw_formatted <- kw_results %>%
  dplyr::mutate(
    statistic = round(statistic, 2),
    df = as.integer(df),
    p_value = round(p_value, 5),
    p_adj_bonferroni = round(p_adj_bonferroni, 5),
    epsilon_sq = round(epsilon_sq, 3)
  )

knitr::kable(
  kw_formatted,
  caption = paste(
    "Kruskal-Wallis tests, Bonferroni-adjusted p-values,",
    "and epsilon-squared effect sizes by age group"
  ),
  col.names = c(
    "Determinant",
    "n",
    "Number of groups",
    "Kruskal-Wallis H",
    "Degrees of freedom",
    "Unadjusted p-value",
    "Bonferroni-adjusted p-value",
    "Epsilon-squared"
  )
)

# ============================================================
# 2. Identify significant omnibus tests
# ============================================================

sig_dets <- kw_results %>%
  dplyr::filter(
    !is.na(p_adj_bonferroni),
    p_adj_bonferroni < 0.05
  ) %>%
  dplyr::pull(Determinant) %>%
  as.character()

print(sig_dets)

# ============================================================
# 3. Dunn post-hoc tests with Bonferroni correction
# ============================================================

if (length(sig_dets) > 0) {

  dunn_results <- purrr::map_dfr(
    sig_dets,
    function(det) {

      # Retain complete observations
      df_sub <- merged_hexad_age %>%
        dplyr::transmute(
          AgeGroup = as.character(AgeGroup),
          Score = suppressWarnings(
            as.numeric(as.character(.data[[det]]))
          )
        ) %>%
        dplyr::filter(
          !is.na(AgeGroup),
          AgeGroup != "",
          !is.na(Score)
        )

      # Dunn test with Bonferroni-adjusted p-values
      dt <- FSA::dunnTest(
        x = df_sub$Score,
        g = df_sub$AgeGroup,
        method = "bonferroni"
      )

      # Sample size for each age group
      group_sizes <- df_sub %>%
        dplyr::count(
          AgeGroup,
          name = "group_n"
        )

      # Extract and process Dunn-test results
      dunn_tbl <- tibble::as_tibble(dt$res) %>%
        dplyr::mutate(
          Determinant = det,

          Group1 = stringr::str_trim(
            stringr::str_split_fixed(
              Comparison,
              " - ",
              2
            )[, 1]
          ),

          Group2 = stringr::str_trim(
            stringr::str_split_fixed(
              Comparison,
              " - ",
              2
            )[, 2]
          )
        ) %>%

        # Add sample size for Group 1
        dplyr::left_join(
          group_sizes,
          by = c("Group1" = "AgeGroup")
        ) %>%
        dplyr::rename(
          n_Group1 = group_n
        ) %>%

        # Add sample size for Group 2
        dplyr::left_join(
          group_sizes,
          by = c("Group2" = "AgeGroup")
        ) %>%
        dplyr::rename(
          n_Group2 = group_n
        ) %>%

        # Calculate pairwise effect-size magnitude
        dplyr::mutate(
          n_pair = n_Group1 + n_Group2,

          effect_r = abs(Z) / sqrt(n_pair),

          significant = P.adj < 0.05
        ) %>%

        # Explicitly use dplyr::select to avoid package conflicts
        dplyr::select(
          Determinant,
          Comparison,
          Group1,
          Group2,
          n_Group1,
          n_Group2,
          n_pair,
          Z,
          P.unadj,
          P.adj,
          effect_r,
          significant
        )

      return(dunn_tbl)
    }
  )

  # Format only after all calculations are completed
  dunn_formatted <- dunn_results %>%
    dplyr::mutate(
      Z = round(Z, 3),
      P.unadj = round(P.unadj, 5),
      P.adj = round(P.adj, 5),
      effect_r = round(effect_r, 3)
    )

  # Table containing all pairwise comparisons
  knitr::kable(
    dunn_formatted,
    caption = paste(
      "Dunn post-hoc comparisons with Bonferroni-adjusted p-values",
      "and pairwise effect sizes by age group"
    ),
    col.names = c(
      "Determinant",
      "Comparison",
      "Group 1",
      "Group 2",
      "n Group 1",
      "n Group 2",
      "Pairwise n",
      "Z",
      "Unadjusted p-value",
      "Bonferroni-adjusted p-value",
      "Effect size r",
      "Significant"
    )
  )

  # Table containing only significant pairwise comparisons
  dunn_significant <- dunn_formatted %>%
    dplyr::filter(significant)

  knitr::kable(
    dunn_significant,
    caption = paste(
      "Significant Dunn post-hoc comparisons after",
      "Bonferroni correction"
    ),
    col.names = c(
      "Determinant",
      "Comparison",
      "Group 1",
      "Group 2",
      "n Group 1",
      "n Group 2",
      "Pairwise n",
      "Z",
      "Unadjusted p-value",
      "Bonferroni-adjusted p-value",
      "Effect size r",
      "Significant"
    )
  )

} else {

  message(
    "No determinants remained significant after the ",
    "Bonferroni correction; Dunn post-hoc tests were not conducted."
  )
}
```






#### Multigroup Confirmatory factor Analysis

```{r  b6}


# Items
hexad_items <- c("A2","A4","D3","D4","F1","F3","P1","P4","R2","R4","S2","S4")

# 6-factor Hexad-12 model
hexad_model <- '
  Achiever       =~ A2 + A4
  Disruptor      =~ D3 + D4
  FreeSpirit     =~ F1 + F3
  Philanthropist =~ P1 + P4
  Player         =~ R2 + R4
  Socializer     =~ S2 + S4
'

merged_hexad_age <- merged_hexad %>%
  filter(!is.na(Age)) %>%
  mutate(
    AgeGroup = case_when(
      Age >= 18 & Age <= 24 ~ "18–24",
      Age >= 25 & Age <= 34 ~ "25–34",
      Age >= 35 & Age <= 49 ~ "35–49",
      Age >= 50             ~ "50+",
      TRUE ~ NA_character_
    ),
    AgeGroup = factor(AgeGroup, levels = c("18–24","25–34","35–49","50+"))
  )

table(merged_hexad_age$AgeGroup)  # 18–24, 25–34, 35–49, 50+


cfa_age_main <- cfa(
  model     = hexad_model,
  data      = merged_hexad_age,
  estimator = "DWLS",
  ordered   = hexad_items
)



cfa_by_age <- merged_hexad_age %>%
  split(.$AgeGroup) %>%
  map(~ cfa(
    model     = hexad_model,
    data      = .x,
    estimator = "DWLS",
    ordered   = hexad_items
  ))

# Extract key fit indices by age group
age_fit_dwls <- map_dfr(names(cfa_by_age), function(g) {
  fm <- fitMeasures(cfa_by_age[[g]], c("cfi","tli","rmsea","srmr"))
  tibble(
    AgeGroup = g,
    CFI      = round(fm["cfi"],   3),
    TLI      = round(fm["tli"],   3),
    RMSEA    = round(fm["rmsea"], 3),
    SRMR     = round(fm["srmr"], 3)
  )
})

#age_fit_dwls


run_mi_age <- function(data, group_var = "AgeGroup", model = hexad_model) {
  df <- data %>%
    filter(!is.na(.data[[group_var]])) %>%
    mutate(!!group_var := factor(.data[[group_var]]))

  # Configural
  fit_config <- cfa(
    model     = model,
    data      = df,
    group     = group_var,
    estimator = "MLR"
  )

  # Metric (equal loadings)
  fit_metric <- cfa(
    model       = model,
    data        = df,
    group       = group_var,
    estimator   = "MLR",
    group.equal = c("loadings")
  )

  # Scalar (equal loadings + intercepts)
  fit_scalar <- cfa(
    model       = model,
    data        = df,
    group       = group_var,
    estimator   = "MLR",
    group.equal = c("loadings","intercepts")
  )

  # Scaled chi-square difference test
  mi_table_raw <- lavTestLRT(fit_config, fit_metric, fit_scalar)

  # Round p-values to 5 decimals
  mi_table <- as.data.frame(mi_table_raw) %>%
    mutate(
      Chisq      = round(Chisq,      3),
      `Chisq diff` = round(`Chisq diff`, 3),
      `Pr(>Chisq)` = round(`Pr(>Chisq)`, 5)
    )

  # Fit indices for each level
  fit_table_raw <- rbind(
    config = fitMeasures(fit_config, c("cfi","rmsea","srmr")),
    metric = fitMeasures(fit_metric, c("cfi","rmsea","srmr")),
    scalar = fitMeasures(fit_scalar, c("cfi","rmsea","srmr"))
  )

  fit_table <- as.data.frame(fit_table_raw) %>%
    rownames_to_column("Model") %>%
    mutate(
      cfi   = round(cfi,   3),
      rmsea = round(rmsea, 3),
      srmr  = round(srmr,  3)
    )

  # Delta CFI (metric vs configural, scalar vs metric)
  delta_cfi <- tibble(
    Comparison = c("metric - config", "scalar - metric"),
    Delta_CFI  = c(
      fit_table_raw["metric","cfi"] - fit_table_raw["config","cfi"],
      fit_table_raw["scalar","cfi"] - fit_table_raw["metric","cfi"]
    ) %>% round(3)
  )

  list(
    config    = fit_config,
    metric    = fit_metric,
    scalar    = fit_scalar,
    mi_table  = mi_table,
    fit_table = fit_table,
    delta_cfi = delta_cfi
  )
}


mi_age <- run_mi_age(merged_hexad_age, group_var = "AgeGroup")

mi_age$mi_table      # LRT with rounded p-values
mi_age$fit_table     # CFI / RMSEA / SRMR by model
#mi_age$delta_cfi     # ΔCFI diagnostics


```

## Country-related patterns in Hexad-12 scores.

#### Appendix A23. Kruskal–Wallis test for Hexad determinants by top 10 countries

```{r}
library(dplyr)
library(purrr)
library(tibble)
library(knitr)

# Hexad determinants
hexad_dets <- c(
  "philanthropist",
  "socializer",
  "freeSpirit",
  "achiever",
  "player",
  "disruptor"
)

# ============================================================
# Kruskal-Wallis tests by country
# ============================================================

kw_country_results <- purrr::map_dfr(
  hexad_dets,
  function(det) {

    # Retain observations with a valid country and determinant score
    df_sub <- hexad_top10 %>%
      dplyr::transmute(
        Country = trimws(as.character(Country)),
        Score = suppressWarnings(
          as.numeric(as.character(.data[[det]]))
        )
      ) %>%
      dplyr::filter(
        !is.na(Country),
        Country != "",
        !is.na(Score)
      )

    # Valid sample size and number of countries
    n_total <- nrow(df_sub)
    n_groups <- dplyr::n_distinct(df_sub$Country)

    # Return missing results if the test cannot be conducted
    if (n_groups < 2 || n_total <= n_groups) {
      return(
        tibble::tibble(
          Determinant = det,
          n = n_total,
          statistic = NA_real_,
          df = NA_real_,
          p_value = NA_real_,
          epsilon_sq = NA_real_
        )
      )
    }

    # Run the Kruskal-Wallis test
    kw <- stats::kruskal.test(
      Score ~ Country,
      data = df_sub
    )

    # Extract the Kruskal-Wallis H statistic
    H <- unname(kw$statistic)

    # Kruskal-Wallis epsilon-squared:
    # epsilon^2 = (H - k + 1) / (n - k)
    epsilon_sq <- (
      H - n_groups + 1
    ) / (
      n_total - n_groups
    )

    # Negative estimates can occur because of sampling variation
    epsilon_sq <- max(0, epsilon_sq)

    # Return unrounded results
    tibble::tibble(
      Determinant = det,
      n = n_total,
      statistic = H,
      df = unname(kw$parameter),
      p_value = kw$p.value,
      epsilon_sq = epsilon_sq
    )
  }
) %>%

  # Apply Bonferroni correction across the six determinant tests
  dplyr::mutate(
    p_adj_bonferroni = stats::p.adjust(
      p_value,
      method = "bonferroni"
    )
  ) %>%

  # Give determinants publication-ready labels
  dplyr::mutate(
    Determinant = factor(
      Determinant,
      levels = hexad_dets,
      labels = c(
        "Philanthropist",
        "Socializer",
        "Free Spirit",
        "Achiever",
        "Player",
        "Disruptor"
      )
    )
  ) %>%

  # Match the column order used in the previous tables
  dplyr::select(
    Determinant,
    n,
    statistic,
    df,
    p_value,
    p_adj_bonferroni,
    epsilon_sq
  )

# ============================================================
# Format values for presentation
# ============================================================

kw_country_formatted <- kw_country_results %>%
  dplyr::mutate(
    statistic = round(statistic, 2),
    df = as.integer(df),
    p_value = round(p_value, 3),
    p_adj_bonferroni = round(p_adj_bonferroni, 3),
    epsilon_sq = round(epsilon_sq, 3)
  )

# ============================================================
# Updated Appendix A23 table
# ============================================================

knitr::kable(
  kw_country_formatted,
  caption = paste(
    "Kruskal-Wallis tests, Bonferroni-adjusted p-values,",
    "and epsilon-squared effect sizes for Hexad determinants",
    "across the top 10 countries"
  ),
  col.names = c(
    "Determinant",
    "n",
    "Kruskal-Wallis H",
    "Degrees of Freedom",
    "p-value",
    "Adjusted p-value",
    "Epsilon-squared"
  ),
  align = c("l", "r", "r", "r", "r", "r", "r")
)
```



#### Multigroup Confirmatory factor Analysis

```{r}


items <- c("P1","P4","S2","S4","A2","A4","R2","R4","F1","F3","D3","D4")


normalize_country <- function(x) {
  x <- stringr::str_trim(as.character(x))
  x <- ifelse(x == "", NA_character_, x)
  # strip qualifiers in parentheses
  x <- sub("\\s*\\(.*\\)$", "", x)
  # standardize a few variants
  dplyr::case_when(
    x %in% c("Perú","Peru") ~ "Perú",
    x == "Estados Unidos de América" ~ "Estados Unidos",
    TRUE ~ x
  )
}

data <- merged_hexad %>%
  dplyr::mutate(Country = normalize_country(Country))


# Map to 3 regions
data <- data %>%
  dplyr::mutate(
    Region3 = dplyr::case_when(
      Country %in% c("Guatemala","Honduras","El Salvador",
                     "Nicaragua") ~ "Central_America_Mex_Caribbean",
      
      Country %in% c("Venezuela","Colombia") ~ "Northern_Andean",
      
      Country %in% c("Argentina","Ecuador","Perú","Bolivia") ~ "Southern_Cone",
      TRUE ~ NA_character_
    )
  ) %>%
  dplyr::filter(!is.na(Region3))

data$Region3 <- factor(data$Region3)

cat("\nCounts per Region3:\n"); print(table(data$Region3))

data <- data %>% filter(if_all(all_of(items), ~ !is.na(.x)))
data[items] <- lapply(data[items], function(x) as.numeric(as.character(x)))


cfa_model <- '
Philanthropist =~ P1 + P4
Socializer     =~ S2 + S4
Achiever       =~ A2 + A4
Player         =~ R2 + R4
FreeSpirit     =~ F1 + F3
Disruptor      =~ D3 + D4
'


# A. Configural Invariance (Baseline)
fit_config <- cfa(
  model = cfa_model,
  data = data,
  group = "Region3",
  estimator = "MLR"
)

# B. Metric Invariance (Constrain Loadings)
fit_metric <- cfa(
  model = cfa_model,
  data = data,
  group = "Region3",
  estimator = "MLR",
  group.equal = c("loadings")
)

# C. Scalar Invariance (Constrain Loadings + Intercepts)
fit_scalar <- cfa(
  model = cfa_model,
  data = data,
  group = "Region3",
  estimator = "MLR",
  group.equal = c("loadings", "intercepts")
)


# Likelihood Ratio Test (Scaled Chi-square difference)
anova_res <- anova(fit_config, fit_metric, fit_scalar)
print(anova_res)

# Extract Fit Indices
get_fits <- function(fit) {
  fitMeasures(fit, c("cfi.robust", "rmsea.robust", "srmr"))
}

fit_table <- rbind(
  config = get_fits(fit_config),
  metric = get_fits(fit_metric),
  scalar = get_fits(fit_scalar)
)

# Rename for clarity
colnames(fit_table) <- c("CFI", "RMSEA", "SRMR")

cat("\nFit Indices (Robust):\n")
print(round(fit_table, 3))



```
